Automatic Parallelization and Transparent Fault Tolerance\\ (New project paper)

### 2016-04-05 pubs/tfp16/paper.tex
one more small fix

Funding for this project has been provided by the DOE NNSA LANL Laboratory
Directed Research and Development program award 20150845ER; the National
Science Foundation Science, Technology, Engineering, and Mathematics Talent
Expansion Program (STEP) program for undergraduate students; and the DOE
Science Undergraduate Laboratory Internship (SULI) program.
%
Los Alamos National Laboratory is managed and operated by Los Alamos National
Security, LLC (LANS), under contract number DE-AC52-06NA25396 for the
Department of Energy’s National Nuclear Security Administration (NNSA).

>>>>

Funding for this project has been provided by the DOE NNSA LANL Laboratory
Directed Research and Development program award 20150845ER; the National
Science Foundation Science, Technology, Engineering, and Mathematics Talent
Expansion Program (STEP) program for undergraduate students; and the DOE
Science Undergraduate Laboratory Internship (SULI) program.
%
Los Alamos National Laboratory is managed and operated by Los Alamos National
Security, LLC (LANS), under contract number DE-AC52-06NA25396 for the
Department of Energy's National Nuclear Security Administration (NNSA).
